\documentclass[11pt,a4paper]{article}
\usepackage{styles/moderncvweb}

\begin{document}
\input{sections/profile}

{\LARGE\bfseries \ProfileName}\par
\vspace{0.15em}
{\large \ProfileTitle}\par
\vspace{0.3em}
\small \ProfileAddress\, | \ProfilePhone\, | \href{mailto:\ProfileEmail}{\ProfileEmail}\, | \href{https://\ProfileGitHub}{\ProfileGitHub}\par

\vspace{1em}

\section{Profile}
Frontend-focused senior web developer with 10+ years of experience building accessible, performant digital products in Angular, React, Next.js, Ionic, and TypeScript. Strong background in design systems, microfrontends, testing, and close collaboration with product and design teams.

\section{Core Skills}
Frontend: Angular, React, Next.js, Ionic, TypeScript, JavaScript, HTML, CSS, Sass, StencilJS, LitElement, Vue, Nuxt\par
Architecture: Design systems, microfrontends, Domain-Driven Design, Feature-Driven Development, reusable component libraries\par
Testing: Storybook, Vitest, Karma, Jasmine, Jest, Testing Library\par
Tools: Git, GitHub, ESLint, Prettier, Docker, CI/CD pipelines, Swagger / OpenAPI, Postman\par
Backend and APIs: Node.js, Express, Spring Boot, REST, JSON, JWT, SQL\par

\section{Work Experience}
\textbf{BrightPixel Studio} --- Senior Frontend Developer \hfill 2022 -- Present\par
Led migration of a marketing platform to Next.js and TypeScript, improving Core Web Vitals and reducing page-load time by 38\%. Built a reusable component library and a Storybook workflow that shortened UI delivery cycles across product squads.\par
\vspace{0.65em}

\textbf{Nova Commerce} --- Web Developer \hfill 2019 -- 2022\par
Developed responsive e-commerce features with React, Redux, and Node.js for multi-market storefronts. Integrated analytics, payment, and CMS APIs while maintaining performance and code quality standards.\par
\vspace{0.65em}

\textbf{Blue Leaf Digital} --- Frontend Developer \hfill 2017 -- 2019\par
Delivered custom brand websites and campaign microsites with a focus on pixel-perfect execution. Collaborated with UX teams to translate visual concepts into scalable interfaces using modular Sass and JavaScript.\par

\section{Selected Projects}
\textbf{Private Banking \& Business (PBB)} --- Angular 16-20, Reactive Forms, Karma/Jasmine\par
Built app and component library from scratch, upgraded Angular 16 to 20, and aligned the front end with Java Spring Boot microservices using DDD patterns, Native Federation readiness, and CI/CD with GitHub Actions.\par
\vspace{0.4em}

\textbf{Saudi National Bank Mobile App (SNB)} --- Ionic, Angular 16/17, RxJS, Reactive Forms\par
Owned maintenance and quality improvements for core journeys including transactions, loans, and payments. Supported the SNB QuickPay companion app with stability-focused fixes and refactors.\par
\vspace{0.4em}

\textbf{Zurich Design System} --- Angular, StencilJS, Storybook\par
Built the design system from scratch, establishing reusable components and shared documentation standards to improve consistency and front-end delivery speed.\par
\vspace{0.4em}

\textbf{Galatea Design System} --- Angular, StencilJS, Storybook, Microfrontends\par
Served as technical lead during first release support, delivered core web components, and implemented the first microfrontend to define the rollout integration pattern.\par

\input{sections/responsibilities-achievements}

\section{Education}
\textbf{B.Sc. in Computer Science}, Simon Bolivar University\par
Focus on software engineering, web technologies, and human-computer interaction with a strong emphasis on product-oriented development.\par

\section{Languages}
Spanish: Native\par
English: Professional working proficiency\par

\end{document}