\section{Selected Projects}

\projectentry{Private Banking \& Business (PBB)}{Angular 16-20, Reactive Forms, Karma/Jasmine}{Internal banking platform delivered at Capgemini for Santander Bank.}
\entrydetail{Built app and component library from scratch, upgraded Angular 16 to 20, and aligned the front end with Java Spring Boot microservices using DDD patterns, Native Federation readiness, and CI/CD with GitHub Actions.}

\projectentry{Saudi National Bank Mobile App (SNB)}{Ionic, Angular 16/17, RxJS, Reactive Forms}{Large-scale banking app at Crealogix for Saudi National Bank across Android and iOS.}
\entrydetail{Owned maintenance and quality improvements for core journeys (transactions, loans, payments) and supported the SNB QuickPay companion app with stability-focused fixes and refactors.}

\projectentry{Zurich Design System}{Angular, StencilJS, Storybook}{Design system initiative delivered at NTT Data for Zurich Insurance.}
\entrydetail{Built the design system from scratch, establishing reusable components and shared documentation standards to improve consistency and front-end delivery speed.}

\projectentry{Galatea Design System}{Angular, StencilJS, Storybook, Microfrontends}{Design system and front-end platform delivered at NTT Data for Banco Sabadell.}
\entrydetail{Served as technical lead during first release support, delivered core web components, and implemented the first microfrontend to define the rollout integration pattern.}

\projectentry{CORDIS}{Angular, Team Leadership}{European Commission research results portal delivered at NTT Data.}
\entrydetail{Led the Angular front-end stream and a junior team, setting technical direction, enforcing code quality, and unblocking delivery across feature releases.}

\projectentry{Banca+}{Ionic, AngularJS}{White-label digital banking product at Synergy-GB for bank-specific deployments.}
\entrydetail{Contributed to configurable architecture for branding, feature tailoring, backend integration reuse, and CI/CD delivery pipelines with Jenkins across multiple banking implementations.}